--- 
title: "Analisis Resiko"
author: "Bakti Siregar"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: ["References/LDAReference2020A.bib"]
biblio-style: econPeriod
link-citations: yes
github-repo: dsciencelabs/Bookdown-Tempalate_R
description: "Loss Data Analytics adalah teks yang interaktif, online, tersedia secara bebas.
   - Versi online akan berisi banyak objek interaktif (kuis, demonstrasi komputer, grafik interaktif, video, dan sejenisnya) untuk mempromosikan pembelajaran yang lebih dalam.
   - Sebagian dari buku ini akan tersedia dalam format pdf untuk pencetakan dengan biaya rendah.
   - Teks online akan tersedia dalam berbagai bahasa untuk mempromosikan akses ke audiens di seluruh dunia."
---

# Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
